\bf\mftitle

### 2011-01-25 doc/jInfer/twostep/twostep.tex
Changed type of arrows to empty for uml-like diagrams

\def\mftitle{jInfer TwoStep simplifier design and implementation}
\def\mfauthor{Michal Klempa, Mário Mikula, Robert Smetana, Michal Švirec, Matej Vitásek}
\def\mfadvisor{RNDr. Irena Mlýnková, Ph.D., Martin Nečaský, Ph.D.}
\def\mfplacedate{Praha, 2011}
\title{\bf\mftitle}
\author{\mfauthor \\ Advisors: \mfadvisor}
\date{\mfplacedate}

@@

\noindent \begin{tabular}{|l|l|} \hline
Responsible developer: & anti \\ \hline
Required tokens:       & cz.cuni.mff.ksi.jinfer.base.interfaces.RuleDisplayer \\ \hline
Provided tokens:       & cz.cuni.mff.ksi.jinfer.base.interfaces.inference.Simplifier \\ \hline
Module dependencies:   & AutoEditor, Base, JUNG, Lookup \\ \hline
Public packages:       & \\ \hline
\end{tabular}

@@

\subsubsection{RegexpAutomatonSimplifier submodule}
TODO anti interface and flow of regexpautomatonsimplifier

\begin{figure}
	\centering\includegraphics[scale=\myscale]{state_removal_modules}
	\caption{Modules of StateRemoval.} \label{state_removal_modules}
\end{figure}
\paragraph{StateRemoval regexp automaton simplifier}
We are using state removal method (see \cite{1224321}) to convert regexp automaton into equivalent regular expression.
This is implemented in \code{StateRemoval} class (on fig. \ref{state_removal_modules}) which implements \code{RegexpAutomatonSimplifier} interface.
We defined one submodule of this class with interface called \code{Orderer}.
It has only one method to implement: \code{getStateToRemove}.
Given automaton it has to return reference to one state which should be removed from automaton at first.
State removal calls this submodule and removes states given until there are only two states in automaton - superInitial and superFinal states,
with exactly one transition.
That transition has final regular expression on it as symbol, it is read and returned to AutomatonMergingState.
We implement one orderer, called \code{Weighted}.
It is simple heuristic - weights all states (weight = sum of {in | out | loop}-transition regular expression lengths) and returns state with lowest weight.

\subsection{RegularExpressionCleaner module}
Last we examine \code{RegularExpressionCleaner} interface.
TODO anti cleaners

>>>>

\def\mftitle{jInfer TwoStepSimplifier design and implementation}
\def\mfauthor{Michal Klempa, Mário Mikula, Robert Smetana, Michal Švirec, Matej Vitásek}
\def\mfadvisor{RNDr. Irena Mlýnková, Ph.D., Martin Nečaský, Ph.D.}
\def\mfplacedate{Praha, 2011}
\title{\bf\mftitle}
\author{\mfauthor \\ Advisors: \mfadvisor}
\date{\mfplacedate}

@@

\noindent \begin{tabular}{|l|l|} \hline
Responsible developer: & Michal Klempa \\ \hline
Required tokens:       & cz.cuni.mff.ksi.jinfer.base.interfaces.RuleDisplayer \\ \hline
Provided tokens:       & cz.cuni.mff.ksi.jinfer.base.interfaces.inference.Simplifier \\ \hline
Module dependencies:   & AutoEditor, Base, JUNG, Lookup \\ \hline
Public packages:       & \\ \hline
\end{tabular}

@@

\subsubsection{RegexpAutomatonSimplifier submodule}
Purpose of \jmodule{RegexpAutomatonSimplifier} is to obtain regular expression from given automaton.
Interface for doing this is thus simple:
\begin{verbatim}
public interface RegexpAutomatonSimplifier<T> {
  Regexp<T> simplify(final RegexpAutomaton<T> inputAutomaton, 
                     final SymbolToString<Regexp<T>> symbolToString) throws InterruptedException;
}
\end{verbatim}
Once again we are encountering \code{symbolToString} with same purpose as before, if submodule would need to present automaton to user
it has to be able to convert symbols of (at runtime) unknown type to strings.

\begin{figure}
	\centering\includegraphics[scale=\myscale]{state_removal_modules}
	\caption{Modules of StateRemoval.} \label{state_removal_modules}
\end{figure}
\paragraph{StateRemoval regexp automaton simplifier}
We are using state removal method (see \cite{1224321}) to convert regexp automaton into equivalent regular expression.
This is implemented in \code{StateRemoval} class (on fig. \ref{state_removal_modules}) which implements \code{RegexpAutomatonSimplifier} interface.
State removal works by removing states of automaton (and redirecting transitions properly) until there are last to two states - superInitial and superFinal.
Both are added before algorithm starts. Former one with $\lambda$-transition to initial state, and from all final states $\lambda$ transition to superFinal state is added.
After removing all states, there is only one transition from superInitial to superFinal state.
That transition has final regular expression on it as symbol, it is read and returned to \jmodule{AutomatonMergingState}.

We defined one submodule of this class with \jmodule{Orderer}.
It has only one method to implement: \code{getStateToRemove}.
Given automaton, it has to return reference to one state which should be removed from automaton at first.
State removal calls this submodule and removes state returned.

\paragraph{Weighted} We implement one orderer, called \code{Weighted}.
It is simple heuristic - weights all states (weight = sum of {in | out | loop}-transition regular expression lengths) and returns state with lowest weight.

\subsection{RegularExpressionCleaner module}
Last we examine \code{RegularExpressionCleaner} interface.
Purpose of this submodule is only to make output regular expression corrections, to make them nicer.
For example it is common that converting automaton to regular expression by state elimination produces nested concatenations such like $(name, (person, id))$.
To convert such expression into $(name, person, id)$, one can implement this interface and connect it to work in chain.
Interface is definition is straightforward:
\begin{verbatim}
public interface RegularExpressionCleaner<T> {
  Regexp<T> cleanRegularExpression(final Regexp<T> regexp);
}
\end{verbatim}
Given regular expression, return regular expression.
Converting of regular expression is commonly a recursive task and all our implementations work this way.
Lets look at them.

\paragraph{NestedConcatention}
This cleaner does exactly what we have just described.
It converts nested concatenations into flat ones.

\paragraph{Null}
This cleaner just returns regexp it receives and does nothing.
Plug this one into chain, if you want to omit this step of inference.

\paragraph{EmptyChildren}
Wipes out regular expressions of type: concatenation, alternation, permutation, which have empty \code{children} member.
For example some pitty inferring method produces unnecessary empty regexps in regexp tree as:
$$
(name, (), (person, id))
$$
There is one empty concatenation/alternation/permutation with no sense.
This is wiped out by this cleaner.

\paragraph{Chained}
Enables user to chain more cleaners with output from first one plugged as input into second one and so one.
Thus regular expression from inference can pass through \jmodule{EmptyChildren} and them through \jmodule{NestedConcatenation} cleaners and then it is returned.
